{\itshape Depicting urban boundaries from a mobility network of spatial interactions: A case study of Great Britain with geo-located Twitter data}

### 2016-07-08 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
home

\section{Background and Related Work}
In real-world geography, urban regions are discrete individuals, with or without physical boundaries separating them~\citep{jiang2015}.
For political and administrative purposes, government agencies define various sets of boundaries to partition the geographical space into units at different spatial scale, for instances, states, counties or census tracts and electoral districts.
However, the spatial extents of these defined units often overlap and agglomerate depending how citizens perceive, organize their image of a city and interact with the urban environments~\citep{lynch1960}.
Connections are made among these units with various human activities crossing the boarders, such as social-economic relations and commute patterns of citizens. 
In such cases, certain groups of units are more strongly connected as clusters than others, and the boarders of agglomeration of these units

how people naturally interact with the space can be in grate importance for decision makers regarding city planning, resource allocation and even marketing campaigns.

Official urban boundaries are defined by government agencies for political and administrative purposes. 
Urban environments are conceptualized as spaces that are recreated and formed by human activities~\citep{schliephake}.
A fundamental question when using the administrative, ``top-down'', approach to defining urban boundaries is whether the outcome reflects the spatial interactions of humans.
These interactions can take the form of trade, commerce, social connections, and political activity across the borders.

@@

Official urban boundaries are defined by government agencies for political and administrative purposes.

@@

@@

@@

>>>>

\section{Background and Related Work}
In real-world geography, urban regions are discrete individuals, with or without physical boundaries separating them~\citep{jiang2015}.
For political and administrative purposes, government agencies define various sets of boundaries to partition the geographical space into units at different spatial scale, for instances, states, counties or census tracts and electoral districts.
However, the spatial extents of these defined units often overlap and agglomerate depending how citizens perceive, organize their image of a city and interact with the urban environments~\citep{lynch1960}.

\citep{vasardani2013}
\citep{hollenstein2010}
\citep{stefanidis2013}

For example, empirical studies have utilized 
Connections are made among these units with various human activities crossing the boarders, such as social-economic relations and commute patterns of citizens. 
In such cases, certain groups of units are more strongly connected as clusters than others, and the boarders of agglomeration of these units
how people naturally interact with the space can be in grate importance for decision makers regarding city planning, resource allocation and even marketing campaigns.

These interactions can take the form of trade, commerce, social connections, and political activity across the borders.

@@

@@

\bibitem[\protect\citeauthoryear{Hollenstein and Purves}{2010}]{hollenstein2010}
Hollenstein, L. and Purves, R., 2010. Exploring place through user-generated content: Using Flickr tags to describe city cores. Journal of Spatial Information Science, 2010(1), pp.21-48.

@@

\bibitem[\protect\citeauthoryear{Stefanidis {\itshape{et~al.}}}{2013}]{stefanidis2013}
Stefanidis, A., Cotnoir, A., Croitoru, A., Crooks, A., Rice, M. and Radzikowski, J., 2013. Demarcating new boundaries: mapping virtual polycentric communities through social media content. Cartography and Geographic Information Science, 40(2), pp.116-129.

@@

\bibitem[\protect\citeauthoryear{Vasardani {\itshape{et~al.}}}{2013}]{vasardani2013}
Vasardani, M., Winter, S. and Richter, K.F., 2013. Locating place names from place descriptions. International Journal of Geographical Information Science, 27(12), pp.2509-2532.
